Instructions for developing new pages for the MarineOmics webpage

### 2023-12-14 DRAFT_DNA_methylation.Rmd
Update DRAFT_DNA_methylation.Rmd

@@

The software used as part of this tutorial is **Bismark Bisulfite Mapper** (@10.1093/bioinformatics/btr167). As with any software it is best to be famililar with the [User Manual](https://rawgit.com/FelixKrueger/Bismark/master/Docs/Bismark_User_Guide.html). The content below will provided with the assumption that the reader has read the manual and is meant to serve as guidance based on experience working with marine invertebrates.

>>>>

### Sequencing Depth

@@

The software used as part of this tutorial is **Bismark Bisulfite Mapper** (@10.1093/bioinformatics/btr167), which is one of the more widely-used alignment softwares for methylation data. Another commonly-used options include bwa-meth (@https://doi.org/10.48550/arXiv.1401.1129) and BSMAP (@https://doi.org/10.1186/1471-2105-10-232) (see @https://doi.org/10.1093/bib/bbab021 and @https://doi.org/10.1016/j.csbj.2022.08.051 for comparisons of these software for plant and mammal species, respectively). As with any software it is best to be famililar with the [User Manual](https://rawgit.com/FelixKrueger/Bismark/master/Docs/Bismark_User_Guide.html). The content below will provided with the assumption that the reader has read the manual and is meant to serve as guidance based on experience working with marine invertebrates.
